Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on Nb and Cu

### 2017-11-21 nb_px_paper/nb_px_paper.tex
Finished section 2.1

In addition to the interest in the production of \ce{^{90}Mo} as an intermediate-energy dosimetry standard, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of a number of isomer-to-ground state ratios.
These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$ m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$ d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$ h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$ d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$ h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$ h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$ m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$ h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.

@@

This target stack was assembled and

>>>>

Measurements of isomer-to-ground state ratios have been used for over 20 years to probe the spin distribution of excited nuclear states in the A$\approx$ 190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
In addition to the interest in the production of \ce{^{90}Mo} as an intermediate-energy dosimetry standard, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of a number of isomer-to-ground state ratios.
These include the \ce{^{52\text{m}}Mn} ($t_{1/2}=21.1\pm0.2$ m; J$^\pi=2^+$) to \ce{^{52\text{g}}Mn}  ($t_{1/2}=5.591\pm0.003$ d; J$^\pi=6^+$), \ce{^{58\text{m}}Co} ($t_{1/2}=9.10\pm0.09$ h; J$^\pi=5^+$) to \ce{^{58\text{g}}Co}  ($t_{1/2}=70.86\pm0.06$ d; J$^\pi=2^+$),  \ce{^{85\text{m}}Y} ($t_{1/2}=4.86\pm0.13$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{85\text{g}}Y}  ($t_{1/2}=2.68\pm0.05$ h; J$^\pi=\sfrac{1}{2}^-$),  \ce{^{87\text{m}}Y} ($t_{1/2}=13.37\pm0.03$ h; J$^\pi=\sfrac{9}{2}^+$) to \ce{^{87\text{g}}Y}  ($t_{1/2}=79.8\pm0.3$ h; J$^\pi=\sfrac{1}{2}^-$),  and \ce{^{89\text{m}}Nb} ($t_{1/2}=66\pm2$ m; J$^\pi=\sfrac{1}{2}^-$) to \ce{^{89\text{g}}Nb}  ($t_{1/2}=2.03\pm0.07$ h; J$^\pi=\sfrac{9}{2}^+$)  ratios \cite{Dong2015,Nesaraja2010,Singh2014,Johnson2015,Singh2013}.

@@

\comment{Confirm beam parameters below, from notebook}

This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a \textred{100 \micro s pulse at a frequency of 1 Hz}, for an anticipated integral current of 205.9 nAh.
The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
The activated foils were cleaned of all surface contamination, and transported to a counting lab for decay spectroscopy, which started approximately 7 hours following end-of-beam.
